6CCS3PRJ \\\vspace{0.5cm} A Pragmatic Infrastructure Modelling and Verification Framework

### 2014-04-21 paper.tex
Architecture and getting started screenshots

@@

>>>>

\subsubsection{Getting Started Guide}

The getting started guide explains how to install and use the management agent, after the steps have been followed, the user will be able to effectively visualise the system under test.

\begin{center}
  \includegraphics[scale=0.28]{web-ui/getting-started.png}
\end{center}

@@

\subsubsection{Architecture Diagrams}

Diagrams are often the best way to express complex services with many dependencies, the Web UI uses D3.js to render Scalable Vector Graphic representations of the modelled system. These diagrams also colour code the status of each component.

\begin{center}
  \includegraphics[scale=0.33]{web-ui/architecture.png}
\end{center}
